---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# brand.yml

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/brand.yml)](https://CRAN.R-project.org/package=brand.yml)
[![r-universe status badge](https://posit-dev.r-universe.dev/brand.yml/badges/version)](https://posit-dev.r-universe.dev/brand.yml)
[![R-CMD-check](https://github.com/posit-dev/brand-yml/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/posit-dev/brand-yml/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Centralize brand guidelines in a single 'brand.yml' file, enabling consistent theming across Quarto, Shiny, R applications, reports, and presentations with minimal configuration.


## Installation

Install the latest release of brand.yml from CRAN with:

```{r}
#| eval: false

install.packages("brand.yml")
```

You can install the development version of brand.yml from [GitHub](https://github.com/) with:

```{r}
#| eval: false

# install.packages("pak")
pak::pak("posit-dev/brand-yml/pkg-r")
```

Alternatively, you can install from [posit-dev.r-universe.dev](https://posit-dev.r-universe.dev/) with:

```{r}
#| eval: false

install.packages(
  'brand.yml',
  repos = c('https://posit-dev.r-universe.dev', 'https://cloud.r-project.org')
)
```

## Example

Use `read_brand_yml()` to read in a brand.yml file into a validated and consistent R list.
You can provide a path to a local file, or `read_brand_yml()` will look for a `_brand.yml` file in your project.

```{r}
library(brand.yml)

brand <- read_brand_yml(
  system.file("examples", "brand-posit.yml", package = "brand.yml")
)

brand$color |> str()
```
